Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-10-02 main_new.tex
Updates from Overleaf

\address{ \\Department of Marine Technology,\\ Trondheim, Norway \\
\printead{e1}}
\address{Department of Mathematical Sciences,\\ Trondheim, Norway\\ \printead{e2}}
\address{Idiap, \\ Martigny, Switzerland, \\
\printead{e3}}
\address{Department of Engineering Cybernetics,\\ Trondheim, Norway \\
\printead{e4}}

>>>>

\address{\\Trygve Olav Fossum \\Department of Marine Technology\\ Otto Nielsens veg. 10, 7491 Trondheim\\ Norway\\
\printead{e1}}
\address{Jo Eidsvik\\Department of Mathematical Sciences\\ Hogskoleringen 1, 7491 Trondheim\\ Norway\\ \printead{e2}}
\address{David Ginsbourger\\ Idiap Research Institute\\ Rue Marconi 19, 1920 Martigny\\ Switzerland\\
\printead{e3}}
\address{Kanna Rajan\\Department of Engineering Cybernetics\\ O. S. Bragstads Plass 2D, 7034 Trondheim\\ Norway\\
\printead{e4}}
